Review Paper Draft

### 2020-06-25 main.tex
Section 2: notes/responses
2.2 edits

The mechanism of environmental confounding is summarized in the directed acyclic graph displayed in figure \ref{fig:ps_env}. The undirected dashed line between population stratification and environmental exposure indicates that while we assume these elements are correlated, we do not assume any causal direction. Otherwise stated, we do not assume that environmental factors influence population-specific allele frequencies, or vice versa, only that the two may be related. Additionally, we assume that the environmental exposure has no effect on on observed SNPs.  \pb{I find these previous two sentences confusing/contradictory: We assume that environment and genetics are related, but also that environment has no effect on SNPs.}

>>>>

The mechanism of environmental confounding is summarized in the directed acyclic graph displayed in figure \ref{fig:ps_env}. The undirected dashed line between population stratification and environmental exposure indicates that while we assume these elements are correlated, we do not assume any causal direction. Otherwise stated, we do not assume that environmental factors \anna{directly} influence population-specific allele frequencies, or vice versa, only that the two may be related. \pb{I find these previous two sentences confusing/contradictory: We assume that environment and genetics are related, but also that environment has no effect on SNPs.}
